A robust framework for variable extrusion width concentric toolpath generation

### 2019-08-05 1_intro.tex
lil goal
lil comments
add a line as goal
zjenja: added goal
lil: update TODOs

\subsection{Goal}
\begin{itemize}
\item Accurate fabrication of thin walls
\item Prevent underfilling and overfilling
\item ... for accurately matching stiffness properties
\item ... and/or translucency properties
\end{itemize}

>>>>

\subsection{Problem}
Too thin lines cannot be fabricated accurately.

\todo{Tim will make pictures of too thin beads and too thick beads.}

Jagged lines cause jerky problems.
Wears down mechanics.
Takes long to print.

\subsection{Goal}
\begin{itemize}
\item added 1 goal
\item zjenja added goal
\item Accurate fabrication of thin walls
\item Prevent underfilling and overfilling
\item ... for accurately matching stiffness properties
\item ... and/or translucency properties
\item Without generating paths smaller than \SI{70}{\percent} of the nozzle size
\item While generating maximally paths of \SI{140}{\percent} of the nozzle size
\end{itemize}

\subsection{Contributions}
\begin{itemize}
\item A framework for generating conentric toolpaths with variable width
\end{itemize}

### 2019-08-05 6_validation.tex
move example shapes to discussion
lil: update TODOs

The overfill regions are calculated by adding the polygonal areas of each extrusion segment to a list.
We then add the original outline shape in reverse and perform a clipper operation which only keeps areas of positive winding order.
Because the reverse outline shape reduces the winding order of all extruded segments by one, we are left with the overfill areas.
In order to estimate the areas which are triply covered by extrusion segments, we repeat the process of adding the outline in reverse and performing the clipper operation.
These tripple extrusion areas count double toward the total amount of overfill.
The resulting overfill and underfill areas are visualzied for the different toolpath strategies in \cref{visualized_accuracy}.

\todo{Visualize results in tables and/or graphs.}

\paragraph{Manufacturability}
Depending on the hardware configuration some bead widths are difficult to manufacture.
A bead width far below the nozzle size can result in fluttered extrusion, while a bead width far above the nozzle size can require pressures above the specifications of the machine.
We visualize the bead widths reslting from the different strategies in an exaggerated manner in \cref{visualized_accuracy}.

Example shapes:
\begin{itemize}
\item same as Moessen: grids of triangular holes
\item same as Moessen: circular holes.
\item same as Jin 
\item same as Kao
\item wedge
\item layer of a typical model: phone case
\item some of the above shapes, but with some fuzzy randomized outline
\end{itemize}

\subsection{Experimentation}
Print objects and show qualities:
\begin{itemize}
\item visual consistency of flat top skin surface
\item visual gradual transparency changes
\item graphs of tensile tests on thin walled object
\end{itemize}

Print on mississipi?

What material should I print with for the tensile tests?

>>>>

The overfill regions are calculated by adding the polygonal areas of each extrusion segment to a list.
We then add the original outline shape in reverse and perform a clipper operation which only keeps areas of positive winding order.
Because the reverse outline shape reduces the winding order of all extruded segments by one, we are left with the overfill areas.
In order to estimate the areas which are triply covered by extrusion segments, we repeat the process of adding the outline in reverse and performing the clipper operation.
These tripple extrusion areas count double toward the total amount of overfill.
The resulting overfill and underfill areas are visualzied for the different toolpath strategies in the top of \cref{visualized_accuracy}.

\todo{Zjenja should visualize overfill and underfill results in tables and/or graphs.}

\paragraph{Manufacturability}
Depending on the hardware configuration some bead widths are difficult to manufacture.
A bead width far below the nozzle size can result in fluttered extrusion, while a bead width far above the nozzle size can require pressures above the specifications of the machine.
\todo{Tim should put pictures of extremal bead widths in introduction!}
We visualize the bead widths resulting from the different strategies in an exaggerated manner in the bottom of \cref{visualized_accuracy}.

\subsection{Experimentation}
\todo{Tim will print objects and show qualities:}
\begin{itemize}
\item visual consistency of flat top skin surface
\item visual gradual transparency changes
\item graphs of tensile tests on thin walled object
\end{itemize}
